Draft Visualizations for Semester Project

### 2018-11-27 Visualizations/Draft Visualizations Template.Rmd
Update Draft Visualizations Template.Rmd

This chi-squared test's p value is very large. Therefore, there is likelt not a relationship between these two variables.

@@

@@

```{r}
#Create Visualization
t4 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap(health$CompanySize~ ., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Company Size") + xlab("Perceived Difficulty Level") + ylab("Count")
t4
```

NOTE:  VE = Very Easy, SE = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, VH = Very Hard, DK = Don't Know.

@@

Because the p value is not less than .01 we cannot reject the null. The null variables is that there is no relationship between these two variables.

@@

Survey respondents in the 17-37 and 37-57 age groups are about evenly split among stating they would feel comfortable discussing a mental health disorder with their supervisor, those who say they would not, and those who say they might. In both cases, the majority say they would feel comfortable.  The next most common response is maybe, and no received the least amount of responses. However, in both cases over a quarter of participants in both age groups answered that they would not feel comfortable.  The 57-77 range has a low number of responses, although in that case "No" is the second most common reponse.  Given the chi-squared test results and the visualization, it does not appear that age has much of an impact on comfort level in discussing a mental health disorder with a supervisor. However, the fact that there are fewer responses from the 37-57 and especially the 57-77 age groups may impact our results.

###Answers by Company Size
```{r}
MHbCS <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$CompanySize)
MHbCS
```

@@

@@

```{r}
MHbPR <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.)
MHbPR
```

@@

###Answers by If They Think Supervisor Would View Them Negatively If They Knew You Suffered From a Mental Health Issue

@@

```{r}
MHCbG <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers., health$gender)
MHCbG
```

@@

@@

@@

>>>>

@@

This chi-squared test's p value is very large. Therefore, there is likely not a relationship between these two variables.

@@

```{r}
#Create Visualization
t4 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap(health$CompanySize~ ., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Company Size") + xlab("Perceived Difficulty Level") + ylab("Count")
t4
```
NOTE:  VE = Very Easy, SE = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, VH = Very Hard, DK = Don't Know.

@@

Because the p value is not less than .01 we cannot reject the null. The null hypothesis is that there is no relationship between these two variables.

@@

The majority of respondents in the 17-37 and 37-57 age groups responded that they would feel comfortable discussing a mental health disorder with their supervisor.  The next most common response is that they might, and no received the least amount of responses from the 17-37 and 37-57 age groups. However, in both cases over a quarter of participants in both age groups answered that they would not feel comfortable.  The 57-77 range has a low number of responses, although in that case "No" is the second most common reponse.  Given the chi-squared test results and the visualization, it does not appear that age has much of an impact on comfort level in discussing a mental health disorder with a supervisor. However, the fact that there are fewer responses from the 37-57 and especially the 57-77 age groups may impact our results.

```{r}
MHbCS <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$CompanySize)
MHbCS
prop.table(MHbCS, 2)
```

@@

Because the p value is not less than .01 we cannot reject the null. The null hypothesis is that there is no relationship between these two variables.

```{r}
t11 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_wrap(health$CompanySize ~., scales="free_y") + ggtitle("Comfort with Discussing MH with Supervisor by Company Size") + xlab("Would you feel comfortable discussing a mental health disorder with your supervisor?") + ylab("Count")
t11
```

The pattern that we see in the data visualization is interesting.  For companies in the 26-100, 100-500, and 500-1000 groups (and to a lesser extent in the 6-25 group), fewer respondents indicate they would not feel comfortable discussing a mental health disorder with their supervisor than selecting the "Maybe" or "Yes" options.  However, in the "More than 1000" group, most respondents indicated they would not feel comfortable (although a significant amount answered "Maybe" or "Yes").  It is possible that for larger companies people may feel less comfortable discussing these issues with supervisors because it the organization is more bureaucratic or there are employee/supervisor relationships that are less personal.  However, it is also possible that these results indicate that the results are depedendent on the company as well as other factors. Because the null is larger than .01, we fail to reject the null that there is a significant relationship between the two variables.

@@

```{r}
MHbPR <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$Do.you.think.that.discussing.a.mental.health.disorder.with.your.employer.would.have.negative.consequences.)
MHbPR
prop.table(MHbPR, 2)
```

@@

###Answers by If They Think Discussing a Mental Health Disorder with Employer Would Have Negative Consequences

```{r}
MHbVN <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$Do.you.think.that.discussing.a.mental.health.disorder.with.your.employer.would.have.negative.consequences.)
MHbVN
```

```{r}
chisq.test(MHbVN)
```

Because the p value is less than .01 we can reject the null and say that we think that there is a statistically significant relationship between these two categories.

```{r}
#Modify Labels for perception of mental health disclosure impact
health$negimp <- factor(health$Do.you.think.that.discussing.a.mental.health.disorder.with.your.employer.would.have.negative.consequences.,
levels = c("Maybe", "No", "Yes"),
labels = c("Maybe Expect a Negative Impact", "Do Not Expect Negative Impact", "Expect Negative Impact"))
#Check Results
table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$negimp)
```

```{r}
t12 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_wrap(health$negimp ~., scales="free_y") + ggtitle("Comfort with Discussing MH with Supervisor by Perception of Negative Impact") + xlab("Would you feel comfortable discussing a mental health disorder with your supervisor?") + ylab("Count")
t12
```

####Interpret Results

The results here are fairly clear.  Most people who responded that they feel that discussing a mental health disorder would have a negative impact also are not comfortable discussing a mental health issue with a supervisor.  The reverse is also true, most people who responded that they do not feel that discussing a mental health disorder would have a negative impact also indicate that they would be comfortable discussing a mental health issue with their supervisor. For those who responded that there maybe a negative impact, most also answered that they may be comfortable discussing a mental health disorder with their supervisor (with "no" being the second most common response for that group).  Therefore, any outreach that we do or program that we plan needs to keep this in mind.

@@

```{r}
MHCbG <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers., health$gender)
MHCbG
prop.table(MHCbG, 2)
```

@@

The chi-squared is very large.  Therefore, we cannot reject the null hypothesis that these categories are independent.

```{r}
t13 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$gender ~., scales="free_y") + ggtitle("Comfort with Discussing MH with Coworkers by Gender") + xlab("Would you feel comfortable discussing a mental health disorder with your coworkers?") + ylab("Count")
t13
```

####Interpret Results

The chi-squared test appears to indicate that there is not a significant relationship between gender and comfort with discussing mental health with coworkers.  However, these results may be impacted by the fact that there are fewer respondents who are female or another gender than men.  However, a higher proportion of female respondents indicate that they do not feel comfortable discussing a mental health disorder with coworkers.  However, across all genders the most common response is "maybe."  This indicates that a lot may depend on their relationships with individual coworkers (e.g., they may feel comfortable with discussing with a specific coworker). Interestingly, as stated above, most respondents across genders indicated that they would be comfortable discussing a mental health disorder with their supervisors.

@@

We get a warning that the approximation may be incorrect, likely because some of the values from the table are small.  However, it potentially indicates that that the differences between age groups is not statistically significant.

```{r}
t14 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$AgeGroup ~., scales="free_y") + ggtitle("Comfort with Discussing MH with Coworkers by Age Group") + xlab("Would you feel comfortable discussing a mental health disorder with your coworkers?") + ylab("Count")
t14
```

####Interpret Results

Members of the 17-37 and 37-57 age group have a similar pattern.  The majority of respondents indicated that they might feel comfortable discussing a mental health disorder with coworkers, with the second most common response being that they would not. When I looked at the comfort level of discussing a mental health disorder with supervisors, the results were different. Interestingly, as stated above, the majority of respondents in the 17-37 and 37-57 age groups responded that they would feel comfortable discussing a mental health disorder with their supervisor. Therefore, there may be a higher comfort level discussing mental health disorders with supervisors than other coworkers (or respondents' comfort level may vary by the coworker).

@@

The chi-squared is less than .01.  Therefore, we can reject the null and say that there is a relationship between these two variables.

####Creating the Visualization

```{r}
t17 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers.))+geom_bar()+facet_wrap(health$Do.you.think.that.team.members.co.workers.would.view.you.more.negatively.if.they.knew.you.suffered.from.a.mental.health.issue. ~., scales="free_y") + ggtitle("Comfort with Discussing MH with Coworkers by Perceived Negative Impact") + xlab("Would you feel comfortable discussing a mental health disorder with your coworkers?") + ylab("Count")
t17
```

In this visualization we see that perceived impact of discussing a mental health disorder with coworkers has a potentially significant impact on comfort level with discussing a mental health disorder with coworkers.  For those who feel that they would be viewed negatively by coworkers if they knew the respondent had a mental health issue, they frequently answer that they would not feel comfortable discussing a mental health disorder with coworkers. For those who feel like they are negatively viewed by coworkers because of a mental health issue, appear to be evenly split between maybe being comfortable and not being comfortable. Meanwhile, for those who feel that they are not viewed more negatively because of a mental health disorder, they most frequently say they would be comfortable discussing mental health with coworkers. For those who did not think they would be viewed negatively, they most frequently select that they may be comfortable discussing a mental health disorder with other coworkers, with yes being the second most common response from that group. This indicates that we may want to consider providing training to employees about mental illness in the workplace.
